(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-05 ms.tex
discussion
initial fpp text

@@

In this paper, we present stellar and planetary parameters for each system.

Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
level. We also are able to confirm \anytodo{Number} of these systems as false positives.

@@

This is Dan. 
[for logic flow, perhaps this section should follow the FP section?]

@@

\section{False Positive Analysis}

As has been well known from the early days of transit searches, it is 
possible for an eclipsing binary star to masquerade as a transiting 
planet if (a) it is a highly grazing eclipse, or (b) the binary system
comprises only a small fraction of the total light in the photometric
aperture, resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, such as high-resolution
imaging or radial-velocity measurements.  
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move 
toward probabilistic interpretation of transit signals, rather than 
comprehensive follow-up of each individual candidate.

@@

@@

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems.
One of these is EPIC 201367065, a three-planet system originally announced by

\citet{Crossfield15}.
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed 
by
\kep \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet 
sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.

>>>>

\newcommand{\Nfp}{$X$}
\newcommand{\Nvalidated}{$Y$}
\newcommand{\Nlimbo}{$Z$}

@@

In this paper, we present stellar and planetary parameters for each system.
Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm 
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
level. We also are able to confirm \anytodo{Number} of these systems as false positives.

@@

This is Dan.

@@

\section{False Positive Analysis}
As has been well known from the early days of transit searches, it is 
possible for an eclipsing binary star to masquerade as a transiting 
planet if (a) it is a highly grazing eclipse, or (b) the binary system
comprises only a small fraction of the total light in the photometric
aperture, resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, such as high-resolution
imaging or radial-velocity measurements.  
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move 
toward probabilistic interpretation of transit signals, rather than 
comprehensive follow-up of each individual candidate.

@@

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new implementation of the \citet{Morton12} procedure, to calculate
the false positive probabilities of each of these K2 candidates,
supplemented in a few cases by high-resolution imaging, where
available.  Table \ref{table:FPP} summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).
We find that \Nfp\ of the presented candidates have false positive
probabilities (FPPs) $>$80\%; these we consider to be likely false
positives.  On the other hand, we find that \Nvalidated\ candidates
have FPP $<$ 1\%; these we consider to be validated planets.  The
remaining \Nlimbo\ candidates have FPPs neither high enough to discard
nor low enough to securely validate.

@@

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems. 
One of these is EPIC 201367065, a three-planet system originally announced by
\citet{Crossfield15}. 
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed by
\kep \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of 
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.
